% !TeX document-id = {a2d44d3b-e138-420b-ae6f-c682fbe88bd4}
% !TeX spellcheck = en_GB
% !TeX encoding = UTF-8
% !TeX TXS-program:quick = txs:///compile | txs:///view

\documentclass[bt]{docstyle/IDSCreport}

\title{Designing a drive-by-wire system}
\subtitle{Changing a go-kart to drive remotely via drive-by-wire}
\authorA{Noah Isaak}
\authorB{Richard Von Moos}
\ethidA{13-929-476}
\ethidB{14-935-740}
\semesterA{5}
\semesterB{6}
\emailA{nisaak@student.ethz.ch}
\emailB{rvmoos@student.ethz.ch}
\supervision{First Supervisor\\ Prof. Dr. Second Supervisor}
\identification{IDSC-XX-YY-ZZ}
\date{Juli 2017}
\keywords{Drive-By-Wire, CANOpen}
\bibliography{IEEEabrv,bibliography}

\begin{abstract}
	The purpose of this work was to design a drive-by-wire system for future use in the field of autonomous self driving cars. The idea of the overall project is to have a fleet of autonomous vehicles, mainly to test fleet management algorithms.
	To realise this, an protoype electric kart will be modified such that all mechanical inputs normally made by a human driving the kart can be made by electric actuators. A kart's size and accessibility to it's components make it easy to modify. With the help of a variety of software, communication between a control unit and the components was set up.  This go-kart prototype was made as a proof of concept and for early testing of the software and hardware. 
\end{abstract}

\begin{document}
\input{chapters/Introduction}
\input{chapters/Hardware}
\input{chapters/Software}
\input{chapters/Communication}
\input{chapters/Implementation}
\input{chapters/Results}
\input{chapters/Conclusion}
\input{chapters/Appendix}
\appendix
\end{document}
